Two Dimensional CSDA at the scale of neuronal tissue.

### 2015-11-11 Reportes/CuadrosPoster.tex
Muchos Registros

>>>>

\begin{figure}
  \includegraphics[width=0.9\textwidth]{LFP_700_more_selected_electrodes_01.svg}
  \caption{LFP recorded from experiment at the onset of the epileptic activity. Selected electrodes from which electrophysiological recording is shown are marked  along various transveral lines to CA. The data is presented as recorded, without any smoothing or denoizing. }
